\documentclass[10pt, twoside, a4paper]{article}
\usepackage[italian]{babel}
%\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{graphicx}
%\usepackage{booktabs}
%\usepackage{wrapfig}
%\usepackage{sidecap}
%\usepackage[small]{caption}
\usepackage{gchords}			%serve per scrivere gli accordi
\setlength{\parindent}{0in}	%serve per togliere l'indentazione della prima riga
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}	%serve per utilizzare i colori \textcolor{blue}{}

\begin{document}

\begin{center}

	\hrule \vspace{0.2cm}
     	\textsc{\LARGE Sex \& Drugs \& Rock \& Roll}
	\vspace{0.2cm} \hrule \vspace{0.2cm}
      	{\large Ian Dury}
      	
\end{center}

%	{\begin{abstract}
%	blablalba
%	 \end{abstract}}

\chords{\chord{4~}{x,p1,p3,p3,p2,p1}{C$\#$m}
		\chord{4~}{p1,p3,p3,p1,p1,p1}{A$\flat$m}
		\chord{4~}{p2,p4,p4,p3,p2,p2}{A}
		\chord{7~}{p1,p3,p3,p2,p1,p1}{B}
		\chord{4~}{x,p2,p4,p4,p4,p2}{D}
%		\chord{7~}{x,p1,p3,p3,p2,p1}{Em} %IIIa pos 
		}
		
Sex and drugs and rock 'n' roll	\hfill	RIFF \\
Is all my brain and body need \\
Sex and drugs and rock 'n' roll \\
Is very good indeed \\

\upchord{C$\#$m}Keep your silly \upchord{A$\flat$m}ways
or \upchord{A}throw them out the win\upchord{B}dow  \\
\upchord{C$\#$m}The wisdom of \upchord{A$\flat$m}your ways
\upchord{A}I've been there and I \upchord{B}know  \\
\upchord{C$\#$m}Lots of other wa\upchord{A$\flat$m}ys,
what \upchord{A}a jolly bad show \upchord{B}\\
\upchord{D}If all you ever do
is \upchord{B}business \upchord{A}you \upchord{G}don't like \\

Sex and drugs and rock 'n' roll	\hfill	RIFF \\
Sex and drugs and rock 'n' roll \\
Sex and drugs and rock 'n' roll \\
Is very good indeed \\

Ev'ry bit of clothing ought to make you pretty \\
You can cut the clothing, grey is such a pity \\
I should wear the clothing of Mr. Walter Mitty \\
See my tailor, he's called Simon \\
I know it's going to fit \\

\upchord{Em}Here's a little bit of advice \\
You're quite welcome, it is free \\
Don't do nothin' that is cut-price \\
You know what they'll make you be \\
They will try their tricky devise \\
Trap you with the ordin'ry \\
Get your teeth into a small slice \\
The cake of liberty \\

\textbf{Solo} \\

Sex and drugs and rock 'n' roll	\hfill	RIFF \\
Sex and drugs and rock 'n' roll \\
Sex and drugs and rock 'n' roll \\
Sex and drugs and rock 'n' roll - ow! ow! \\
Sex and drugs and rock 'n' roll - ow! ow! ow! ow! \\
Sex and drugs and rock 'n' roll .... \\

Peace. \\

\end{document}